Flavour Symmetry Embedded - GLoBES (FaSE-GLoBES)

### 2020-06-05 doc/paper.tex
update tex

\section{Model testing}
{\color{blue}[changing models for demo]}
\begin{figure}[!h]
 \centering
\includegraphics[width=0.48\textwidth]{Figs/TM1_th23_dCP.pdf}
\includegraphics[width=0.48\textwidth]{Figs/OP_th23_dCP.pdf}
\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L. on the plane of true values of $\theta_{23}$ and $\delta$ for TM1 sum rule (left) and a $S_4\otimes H_\text{CP}$ model (right) with DUNE and MOMENT. }
%\caption{\label{fig:th23_delta}The 2-D exclusion contour for sub-models of tri-direct littlest seesaw on the plane of two true standard parameters $\theta_{23}$ and $\delta$, from $1\sigma$ to $5\sigma$, for DUNE (dotted) and MOMENT (solid). The range for each parameter is taken according to the $3\sigma$ uncertainty in NuFit4.0 results. The black dot denotes the best fit of NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)=(33.82^\circ,~8.61^\circ,~49.6^\circ,~215^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$), while the star is the prediction by the tri-direct littlest seesaw model with NuFit4.0 results ($(\theta_{12},~\theta_{13},~\theta_{23},~\delta,~\Delta m_{21}^2,~\Delta m_{31}^2)\sim(36.25^\circ,~8.63^\circ,~47^\circ,~279^\circ,~7.39\times10^{-5}~\text{eV}^2,~2.525\times10^{-3}~\text{eV}^2)$).}
\end{figure}

{\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
In Fig.~\ref{fig:th23_delta}, we present testing {\color{blue}atmospherical sum rule TM1~[cite] (left) and a $S_4\otimes H_\text{CP}$ model broken to $G_e=Z_3$ and $G_\nu=Z_2\otimes H_{\text{CP}}$~[cite] (right)} in various true values of $\theta_{23}$ and $\delta$. 
We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied. In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code. 
%
%
%{\color{blue}And, true values of the other oscillation parameters are fixed at the best fit of NuFit4.0, and this setup is different from the left panel, in which we fix the other oscillation parameters at the model prediction for the true value.}
%
%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}. 
%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
%Here the number \texttt{dof} is $2$. 
%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
More details are presented in the user manual. 
%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.

>>>>

\section{Model testing}
\begin{figure}[!h]
 \centering
\includegraphics[width=0.48\textwidth]{Figs/TM1_th23_dCP.pdf}
\includegraphics[width=0.48\textwidth]{Figs/OP_th23_dCP.pdf}
\caption{\label{fig:th23_delta}Examples for using \textbf{FaSE-GLoBES} to obtain the 2-D exclusion contour at $99\%$ C.L. on the plane of true values of $\theta_{23}$ and $\delta$ for TM1 sum rule (left) and a $S_4$ modular symmetry model (right) with DUNE and MOMENT. }
\end{figure}

{\color{blue}We can also study on how much a neutrino mass model  or a sum rule can be excluded, assuming different true values for oscillation parameters.}
In Fig.~\ref{fig:th23_delta}, we present testing {\color{blue}trimaximal mixing TM1~\cite{Albright:2008rp} (left) and a $S_4$ modular symmetry model~\cite{deMedeirosVarzielas:2019cyj} (right) in various true values of $\theta_{23}$ and $\delta$. TM1 implies three equivalent relations between $\theta_{12}$ and $\theta_{13}$~\cite{Albright:2008rp} :
\begin{eqnarray}\label{eq:TM1}
\tan\theta_{12}=\frac{1}{2}\sqrt{1-3s^2_{13}},&\sin\theta_{12}=\frac{1}{3}\frac{\sqrt{1-3s_{13}^2}}{c_13},&\text{or}~\cos\theta_{12}=\sqrt{\frac{2}{3}}\frac{1}{c_{13}}.
\end{eqnarray}
and also the dependence of $\delta$ on $\theta_{13}$ and $\theta_{23}$:
\begin{eqnarray}\label{eq:TM1_dCP}
\cos\delta=-\frac{\cot 2\theta_{23}(1-5s_{13}^2)}{2\sqrt{2}s_{13}\sqrt{1-3s_{13}^2}}.
\end{eqnarray}
The other model, we use for demonstration, is based on three moduli with finite modular symmetries $S_4^A$, $S_4^B$, and $S_4^C$, associated with two right-handed neutrinos and the charged lepton sector, respectively~\cite{deMedeirosVarzielas:2019cyj}. This model predicts the neutrino mass matrix: 
\begin{eqnarray}
m_\nu=&(\mu_1\hat{c}_R^2+\mu_2\hat{s}_R^{*2})\left(
\begin{array}{ccc}
1& -2\omega^2& -2\omega\\
-2\omega^2&4\omega&4\\
-2\omega&4&4\omega^2
\end{array}
\right)+
(\mu_1\hat{s}^2_R+\mu_2\hat{c}_R^{*2})\left(
\begin{array}{ccc}
0& 0& 0\\
0&1&-1\\
0&-1&1
\end{array}
\right) \nonumber \\
&+(\mu_1\hat{c}_R\hat{s}_R-\mu_2\hat{c}^*_R\hat{s}_R^*)\left(
\begin{array}{ccc}
0& -1& 1\\
-1&4\omega^2&2i\sqrt{3}\\
1&2i\sqrt{3}&-4\omega
\end{array}
\right),
\end{eqnarray}
where $\hat{c}_R$ and $\hat{s}_R$ are $\cos\theta_R\times \mathrm{e}^{i\alpha_2}$ and $\sin\theta_R\times \mathrm{e}^{i\alpha_3}$, respectively. As $\omega$ is fixed at $-\frac{1}{2}+i\frac{\sqrt{3}}{2}$, this model has 5 model parameters: $\mu_1,~\mu_2,~\theta_R,~\alpha_2,~\alpha_3$.
}

We compute the minimal $\chi^2$ value for the model, and allowed all model parameters varied, with the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results.
%In the left panel, we include the prior in Eq.~(\ref{eq:prior}) according to NuFit4.0 results, while in the other one, we do not include priors.
In addition, the studied statistics function is exactly given by Eq.~(\ref{eq:chi-squared}), but the true event rate $n_i$ is predicted by a set of oscillation parameters, which will be varied in the code. 
%
%
%{\color{blue}And, true values of the other oscillation parameters are fixed at the best fit of NuFit4.0, and this setup is different from the left panel, in which we fix the other oscillation parameters at the model prediction for the true value.}
%
%As mentioned in Sec.~\ref{sec:chi-squared}, the user needs to consider Wilk's theorem with the different of degrees of freedom between the {\color{blue}assumed} true theory {\color{blue}($\vec{\theta}^{true}_{OSC}$)} and the hypothesis {\color{blue}($\vec{\theta}^{hyp}_{Model}$)}, \texttt{dof}. 
%{\color{blue}`The assumed true theory' here means that the oscillation parameters assumed for predicting the true event spectrum.} \textcolor{red}{[JT: what is the meaning of the true theory?]} 
%Here the number \texttt{dof} is $2$. 
%And that is our output: \texttt{gsl\_cdf\_chisq\_Qinv(gsl\_cdf\_chisq\_Q(fabs(res),dof),1)}. \textcolor{red}{[I don't understand this sentence.]} 
More details are presented in the user manual. 
%The code for this example is provided as \textbf{th23\_delta.c} in the \textbf{FaSE} distribution.
